SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
adding CSP - the observations should be updated though

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

@@

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.65]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
\end{figure*}

@@

  \multirow{12}{*}{Policy Enforcement}

@@

@@

@@

@@

We group our key observations on the~34 publications along the
dimensions we identified in Section~\ref{sec:dimensions}.

@@

Despite many approaches that have been developed,
application attacks based on code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
malicious source code to applications by using a
variety of languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
even if some of them share characteristics
(for instance, {\sc html} sanitization and {\tt eval} handling)
with supported frameworks like Mozilla's Content Security
Policy~\cite{cspMoz} ({\sc csp}) and Google Caja~\cite{M06,caja}
the majority of them are not used in practice.

>>>>

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

@@

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.65]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
\end{figure*}

@@

  \multirow{13}{*}{Policy Enforcement}

@@

  &   {\sc csp}~\cite{SSM10} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\

@@

A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
is currently supported by many browsers to detect
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not. Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.

@@

  &   {\sc csp}~\cite{SSM10} & {\bf AO} & {\bf AO} & {\sc na} \\

@@

We group our key observations on the~35 publications along the
dimensions we identified in Section~\ref{sec:dimensions}.

@@

Despite many approaches that have been developed,
application attacks based on code injection
have been consistently present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
malicious source code to applications by using a
variety of languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, during the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
even if some of them share characteristics
(for instance, {\sc html} sanitization and {\tt eval} handling)
with supported frameworks like Mozilla's {\sc csp}
and Google Caja~\cite{M06,caja}
the majority of them are not used in practice.
